\jaxcosmo: End-to-End Differentiable and GPU Accelerated Cosmology Library

### 2022-05-31 paper.tex
avoid double citation of CCL and halofit model

%
%\subsection{Validation against the Core Cosmology Library (CCL)}
To illustrate the different features available with the present version of the library, we have written a  notebook to make  comparison with the well established  Core Cosmology Library \citep{2019ApJS..242....2C}. As an example, the Figure \ref{fig:halofit_comparison} shows an example of the non linear matter power spectrum computation using the \texttt{halofit} fitting function \citep{2012ApJ...761..152T, 2003MNRAS.341.1311S}. 
%
\begin{figure}[ht]
    \centering
    \includegraphics[width=\columnwidth]{figures/halofit_pk.png}
    \caption{Comparison of matter power spectrum between CCL and jax-cosmo. \textbf{Example of validation plot} \nblink{CCL_comparison}}
    \label{fig:halofit_comparison}
\end{figure}

>>>>

%
%\subsection{Validation against the Core Cosmology Library (CCL)}
To illustrate the different features available with the present version of the library, we have written a  notebook to make  comparison with the well established  Core Cosmology Library. As an example, the Figure \ref{fig:halofit_comparison} shows an example of the non linear matter power spectrum computation using the \texttt{halofit} fitting function. 
%
\begin{figure}[ht]
    \centering
    \includegraphics[width=\columnwidth]{figures/halofit_pk.png}
    \caption{Comparison of matter power spectrum between CCL and jax-cosmo. \textbf{Example of validation plot} \nblink{CCL_comparison}}
    \label{fig:halofit_comparison}
\end{figure}
